Untitled

### 2024-11-19 code/manuscript_altanalysis.Rmd
new figures

@@

df.temptemp %>% 
  filter(Tx == 1 & Closed == 100 & value > 2)

@@

>>>>

## Formal Pre-trends

pretrends <- c(0,0,0,0,0)
for (k in 1:23){

  #df.temptemptemp <- df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx)) #%>% group_by(ID) %>% mutate(EarlyHHI = first(ClinicHHI, na_rm = TRUE)) %>% filter(EarlyHHI < 9000)
  df.temptemptemp <- df.temptemp %>% mutate(Tx = ifelse(Year >= Att & Att %notin% c(0, 2009, 2010), 1, 0)) %>% filter(!is.na(Tx)) #%>% filter(Att %notin% c(2011))
  colnames(df.temptemptemp)[(16+k)] <- "Outcome"
  # Winsorized
  outlier.vals <- quantile(df.temptemptemp$Outcome, p = c(0.01, 0.99), na.rm = TRUE)
  df.temptemptemp <- df.temptemptemp %>% 
    mutate(Outcome = ifelse(Outcome <= outlier.vals[1], outlier.vals[1], 
                            ifelse(Outcome >= outlier.vals[2], outlier.vals[2], Outcome)))
  model <-  did2s(
      data = df.temptemptemp, 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year , 
        second_stage = ~ i(year.rel, ref = FALSE),
        cluster_var = "ID",
      verbose = TRUE
    )

pretrends <- rbind(pretrends, cbind(Outcome = colnames(df.temptemp[,(16+k)]), model$coeftable))
}

pretrends <- pretrends[-1,]

rownames(pretrends)
ordering <- as.numeric(gsub(pattern = "year.rel::", replacement = "", rownames(pretrends)))

cbind(ordering, data.frame(pretrends))[order(ordering),] %>% 
  filter(ordering %in% c(-6:-2)) %>% 
  filter(Outcome %notin% c("htn.rate","dm.rate","pap.rate","crc.rate","childbmi.rate","adultbmi.rate")) %>% 
  arrange(`Pr...t..`) %>% 
  mutate(P.value = as.numeric(`Pr...t..`)) %>% 
  cbind(c(1:85) / 85 * 0.1) %>% 
  mutate(Row = row_number()) %>% 
  ggplot(aes(x = Row, y = P.value)) + geom_point() + 
  ylab("p-values") + xlab("Significance Rank") + geom_abline(slope = 1/85 * 0.1, intercept = 0, color="red", linetype="dashed", alpha=.5) + theme_minimal() + 
  geom_abline(slope = 1/85, intercept = 0, color="blue", linetype="dashed", alpha=.5)

@@

df.temptemp %>% 
  filter(Tx == 1 & Closed == 100 & value > 2)
```

## Stratified figure instead of table 
```{r}

strat.temp <- coeffs.did.strat
strat.temp[3,] <- strat.temp[3,] / 1000
strat.temp[23,] <- strat.temp[23,] / 100
strat.temp[18,] <- strat.temp[18,] / 100

strat.temp <- (cbind(core.did.estimates.strat[,1], strat.temp[-1,c(1:2)]) %>% 
  data.frame() %>% 
  mutate(Estimate = as.numeric(Estimate), 
         `Std..Error` = as.numeric(Std..Error)) %>% 
  mutate(LB = Estimate - Std..Error * 1.96, 
         UB = Estimate + Std..Error * 1.96) %>% 
  rename(Outcome = V1) %>% 
  mutate(Class = "First Shock"))[c(1, 2, 3, 4, 11:13, 16:23),c(1,2, 4:6)] %>% 
  rbind((cbind(core.did.estimates.strat[,1], strat.temp[-1,c(5:6)]) %>% 
  data.frame() %>% 
  mutate(Estimate = as.numeric(Estimate), 
         `Std..Error` = as.numeric(Std..Error)) %>% 
  mutate(LB = Estimate - Std..Error * 1.96, 
         UB = Estimate + Std..Error * 1.96) %>% 
  rename(Outcome = V1) %>% 
  mutate(Class = "Multiple Shocks"))[c(1, 2, 3, 4, 11:13, 16:23),c(1,2, 4:6)])

strat.temp %>% 
  mutate(Measure = ifelse(Outcome %in% c("Qcomp","Total","Altman","logPatsPerStaff","Staff","Closed"), "Overall Metrics", 
                          ifelse(Outcome %in% c("Pct.MCD","Pct.None","Complexity","Intensity"), "Patient Mix", "Financials"))) %>%

ggplot(aes(y=Outcome, x=Estimate, xmin=LB, xmax=UB)) +
geom_point() +

#this changes the features of the overall effects
#one could resize, reshape, or recolor these points if desired
xlab("Effect Estimates") + 
ylab(NULL) + 
#adds the CIs
geom_errorbarh(height=.1) +

#sets the scales
#note that I reverse the y axis to correctly order the effect #sizes based on my index variable
#scale_x_continuous(limits=c(-2.5,1), breaks = c(-2.5:1), name=xname)+
#scale_y_continuous(name = "", breaks=1:9, labels = t9.forest$X1, trans="reverse")+

#adding a vertical line at the effect = 0 mark
geom_vline(xintercept=0, color="black", linetype="dashed", alpha= 1)+

#faceting based on my subgroups
  #facet_wrap(~X1) +
facet_grid(Measure~Class, scales= "free_y", switch = 'y', space = "free_y") +

#thematic stuff
#ggtitle("Figure 3 - ATT Estimates by SubGroups")+
theme_tufte_revised()+
   theme(strip.placement = "outside") +
#theme(text=element_text(family="Times",size=12, color="black"))+
theme(panel.spacing = unit(1, "lines"))

#core.did.estimates.strat[,1] <- c("Composite Quality of Care, %","Total Patients, No.","Financial Resilience","Operational Efficiency","Clinical Complexity","Intensity","Medicaid, %","Uninsured, %","Cost Per Patient")

@@

## Sites and Zips per clinic
```{r}

df.z.temp %>% 
  filter(Year == 2012) %>% 
  mutate(Treat = ifelse(Att > 0, 1, 0)) %>% 
  group_by(`BHCMIS ID`) %>% #, Treat
  filter(Sites > 0) %>% 
  summarise(Zips = n(), Sites = sum(Sites, na.rm = TRUE)) %>% 
  ungroup() %>% 
  #group_by(Treat) %>% 
  summarise(mean(Zips), mean(Sites))
